---
title: "7/22SacCer"
author: "Erin Smith"
date: "7/22/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
---
# liftOver() from sacCer1 WIG (nucleosome occupancy data) to sacCer3 genome
In order to merge the two genome data sets so I can work with sacCer3 version in the future:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/erinsmith/researchlab") 
?`liftOver,GenomicRanges,Chain-method`
?import.chain
wig_path<-file.path("/Users/erinsmith/researchlab", "nucdata.wig")
nucdatafinal<-import(con=wig_path, seqinfo=seqinfo(genome="sc"))
seqnames(nucdatafinal)
ranges(nucdatafinal)
colnames(nucdatafinal)
chain<-import.chain("/Users/erinsmith/researchlab/sacCer1ToSacCer3.over.chain")
merged<-as.data.frame(liftOver(nucdatafinal,chain))

```
# vmatchPattern() of merged dataframe to find consensus motifs and store start position, end position, and chromosome
How to add motif to each data point? 
Search negative strand for 1 bp off motifs?
```{r pressure, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Biostrings)
?vmatchPattern
saccer3genome<-import("sacCer3.fa",format="FASTA")
consensusdata<-vmatchPattern("CACGTG",saccer3genome,max.mismatch=0,min.mismatch=0,with.indels=FALSE,fixed=TRUE,algorithm="auto")
head(consensusdata)
mismatchconsensusdata<-vmatchPattern("CACGTG",saccer3genome,max.mismatch=1,min.mismatch=1,with.indels=FALSE,fixed=TRUE,algorithm="auto")
```
 # Merge chromosome tables of consensus data to one large table of all chromosomes
 ```{r}
mergedCD<-merge(consensusdata$chrI, consensusdata$chrII, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrIII, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrIV, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrV, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrVI, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrVII, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrVIII, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrIX, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrX, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrXI, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrXII, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrXIII, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrXIV, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrXV, all=TRUE)
mergedCD<-merge(mergedCD, consensusdata$chrXVI, all=TRUE)
head(mergedCD)
```
